The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-02-09 paper/main.tex
commented another possible Γ_a for model 1
incorporate KM's edits
"one star, one planet" section starts by focusing on apparent occurrence
rates.

then, in the next subsection it does rate densities.

then we ease into the general formula, presenting a pseudo-derivation.

The astronomers then assume that all stars are single.  In particular
they do not have accurate enough parallaxes to tell that some of the
stars are apparently overluminous.  They want to compute the number of
planets with size $r$ per star of mass $M$.  If the total number of
stars for which such planets could be detected ($N_\star$) and the
number of detected planets ($N_{\rm det}$) are both large, then the
astronomers' estimate for the occurrence rate ($\Lambda$) is simply
\begin{equation}
\Lambda(r,M) = \frac{N_{\rm det}(r,M)}{N_\star(r,M)}
                    \times \frac{1}{p_{\rm tra}(r,M)},
\label{eq:occ_rate_simple}
\end{equation}
where $p_{\rm tra}$ is the geometric transit probability, needed to
account for the fact that most planetary orbits are not aligned close
enough with our line of sight to produce transits.

@@

Since the effects of binarity are most pronounced when the two
components are similar, we begin by considering a universe in which
all stars are identical, with mass $M$, radius $R$, and luminosity
$L$.  Some fraction of them exist in twin binaries.  All planets have
size $r\p$.  Our goal is to compare the occurrence inferred by
observers who ignore binarity with the true occurrence in single star
systems.

To clarify our terminology, we define ``apparent properties'' as the
properties that one would infer about a system under the assumption
that the host star is single. For instance, the  ``apparent planet
radius'', $r\a$, is the planet radius that one would infer from a
transit signal, assuming that the host star is single.  The observed
transit depth is given by the ratio of the apparent planet radius and
the apparent stellar radius, $R\a$:
\begin{equation}
  \delta_{\rm obs}
  = \left(\frac{r\a}{R\a}\right)^2
  = \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over
          L_{\rm sys}},
  \label{eq:delta_obs_general} 
\end{equation}
for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the host
star's radius (luminosity), and $L_{\rm sys}$ the entire system's
luminosity.  In the example at hand, $R_{\rm host} =R\a = R$, since
all stars have the same size. For single star systems we have
$r=r\a=r\p$. In twin binaries, $r\a=r\p/\sqrt{2}$, since $L_{\rm
sys}=2L$.

We can now understand that the observers are unwittingly reporting an
{\it apparent} occurrence rate $\Lambda\a(r\a)$, a function of
apparent radii.  The apparent occurrence rate is the same as the {\it
true} occurrence rate for transit signals of amplitude $\delta_{\rm
obs} = (r\a/R\a)^2$, but this latter quantity is less astrophysically
significant.

Finally, it is helpful to introduce an apparent rate density
$\Gamma\a$, the average number of planets per star per unit apparent
planet radius. Analogous to Equation~\ref{eq:occ_rate_simple},  
\begin{equation}
  \Gamma\a(r\a) = \frac{n_{\rm det}(r\a)}{N_\star(r\a)}
      \times \frac{1}{p_{\rm tra}(r\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}={\rm d}N_{\rm det}/{\rm d}r\a$ is the number  of
detected planets, per unit $r\a$, with apparent radius $r\a$.  In
Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on
stellar mass since all stars in this model have the same properties.

To compute the number of detected planets, we consider the volumes
within which a signal of a given depth could be detected. At a fixed
signal-to-noise floor, there is a maximum searchable
distance~\citep{pepper_using_2003,pepper_searching_2005}.  From
Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales
as
\begin{equation}
    d \propto \delta_{\rm obs} \cdot L_{\rm sys}^{1/2}.
\end{equation}
Assuming that stars are uniformly distributed in space, the number of
searchable stars $N_\star$ is then proportional to
\begin{equation}
    N_\star \propto n \delta_{\rm obs}^3 L_{\rm sys}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n$ is the number per unit volume of {\it e.g.}, single star, or
binary systems.  We neglect the dependence of $n$ on stellar type.

@@

The searchable volumes for this example are illustrated in
Figure~\ref{fig:model_1_volumes}.  At an apparent radius equal to the
true radius ($r\a=r\p$), single stars with $d<d_0$ are by definition
searchable.  Binaries with $r\a=r\p$ are also searchable, out to
$\sqrt{2}d_0$.  However, in this example no such systems exist; all
planets in twin binaries have true radii $r=r\p$, and so are observed
with apparent radii $r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.  At an
apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets
with true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no
such systems in this model.

How many planets are detected?  If we assume that there are
$N_\star^0(r\a)$ singles that are searchable for planets with $r\a$,
and that there are $Z_0$ planets per single, then single stars
contribute
\begin{equation}
n_{\rm det}^0(r\a) = 
  N_\star^0(r\a) Z_0 p_{\rm tra} \cdot \delta(r\a - r_p)
\end{equation}
planet detections (per unit $r\a$), for $\delta$ the Dirac delta
function.

We can similarly compute the number of planet detections from
binaries.  First though, we define a ratio $\mu \equiv N_\star^{\rm
b}(r\a) / N_\star^0(r\a)$ between the number of searchable binary
systems and the number of searchable singles at any $r\a$.  This
quantity is useful because although $N_\star^{\rm b}$ and $N_\star^0$
vary as a function of the observed transit depth, $\mu$ remains fixed.
Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will
come from primaries,
\begin{equation}
n_{\rm det}^1(r\a) =
    \mu N_\star^0(r\a) Z_1 p_{\rm tra}
    \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
and some from secondaries,
\begin{equation}
n_{\rm det}^2(r\a) = 
    \mu N_\star^0(r\a) Z_2 p_{\rm tra}
    \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
where $Z_1$ is the number of planets per primary, $Z_2$ is the number
of planets per secondary, and $p_{\rm tra}$ is the same for identical
stars.  For twin binaries, Equation~\ref{eq:N_searchable_prop} gives
$\mu = 2^{3/2} n_{\rm b}/n_{\rm s}$, where $n_{\rm b}$ is the number
density of binaries in a volume-limited sample.

The last item we need to write down the apparent rate density
$\Gamma\a(r\a)$ is the number of unresolved point-sources on sky that
the observer thinks are searchable, $N_\star$.  From the definition of
$\mu$,
\begin{equation}
    N_\star(r\a) = N_\star^0(r\a) \times (1 + \mu)
    \label{eq:apparentlysearchable_to_searchable}
\end{equation}
relates the number of apparently searchable point-sources and the
number of searchable singles.  There are in fact $N_\star^0(r\a)\times
(1 + 2\mu)$ searchable stars at any given $r\a$; the observers are
under-counting.

Using Equation~\ref{eq:apparent_rate_density}, the apparent rate
density reported when ignoring binarity is
\begin{align}
    \Gamma\a(r\a) = 
    \frac{1}{1+\mu} Z_0 \cdot
    \delta(r\a-r\p)  +
    \frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
    \delta\left(r\a-\frac{r\p}{\sqrt{2}} \right).
    \label{eq:model_1_apparent_rate_density}
\end{align}
The first term is from singles, and the second is from binaries.  The
number of searchable singles at a given apparent radius,
$N_\star^0(r\a)$, makes no appearance.  The observer has erred in
Equation~\ref{eq:model_1_apparent_rate_density} by under-counting the
number of searchable stars at any apparent radius, and by inferring
incorrect planet radii in binary systems.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Apparent occurrence rate $\Lambda\a$, and occurrence rate for
        singles $\Lambda_0$, for a model with one type of star, one
        type of planet, and twin binaries (same as
        Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
        fraction of $0.1$, and that single, primary, and secondary
        stars host planets at equal rates.  If the true planet radius
        is $r\p$, all planets detected in binaries will have apparent
        radii $r\a = r\p/\sqrt{2}$;
        Equation~\ref{eq:model_1_apparent_rate_density} gives the
        normalizations.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

To assess the severity of these errors, we must assume both a binary
fraction, and also the true number of planets per single, primary, and
secondary star ($Z_0,Z_1,Z_2$).  For the
former,~\citet{raghavan_survey_2010} found a multiplicity fraction of
0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.  By
multiplicity fraction, they meant ``fraction of systems in a
volume-limited sample that are multiple'', which we simplistically
conflate with the fraction of systems in a volume-limited sample that
are binaries:
\begin{equation}
    {\rm binary\ fraction} \equiv \frac{n\b}{n\s + n\b} = 0.44,
\end{equation}
Of course not all of these are binaries are close to being ``twin''
binaries as we have assumed in our simple calculation.  Perhaps only a
tenth of them have pairs of stars close enough in their basic
properties to produce errors as significant as those we have been
considering.  Thus, an appropriate estimate for the binary fraction is
of order $0.05$.  The ratio of the apparent to single star rate
densities,
\begin{equation}
    X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)}
      \right|_{r\a \rightarrow r},
\end{equation}
can then be evaluated as a ``correction factor''.  At the true planet
radius, $X_\Gamma(r\p)=1/(1+\mu)$.  This yields a correction
$X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).  All
together the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is
characteristic of many of our more complicated models, as well.

An alternative assumption is that secondaries do not host planets. In
that case, the correction to the rate density at the true planet
radius becomes $X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.  This gives a
correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
Although the secondaries certainly should have planets, the
sensitivity of $\Gamma\a/\Gamma_0$ to the relative number of planets
per single, primary, and secondary will also become important as we
proceed.

\subsection{One type of star, two types of planets}

@@

Following an identical line of reasoning as in
Section~\ref{sec:model_1}, the apparent rate density can be written
\begin{align}
    \notag
    \Gamma\a(r\a) &=
    \frac{1}{2(1+\mu)} \left[
    Z_0 \cdot \delta(r\a - r\p)
    +
    \left[Z_0 + \mu (Z_1 + Z_2)
    \right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
    \right. \\
    &\quad\quad\quad\quad\quad\quad\quad\quad+
    \left.
    \mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
    \right].
    \label{eq:two_radii_twins}
\end{align}
Just as in Equation~\ref{eq:model_1_apparent_rate_density}, the
$N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
However, there are now three detected planet sizes.  Also different is
that two populations contribute at $r\a = r\p/\sqrt{2}$: the first
population is singles with $r=r\p/\sqrt{2}$, and the second is twin
binaries with $r=r\p$.  Both populations are detected out to the same
maximum searchable distance.  More generally, at any given apparent
radius, there will be contributions from both singles, primaries, and
secondaries~---~but the relative weights between these contributions
will depend on the underlying occurrence rates.

@@

To generalize the procedure of Section~\ref{sec:simplest}, we consider
an SNR-limited transit survey in which the singles and primaries can
have arbitrary properties, but their true masses are known by the
observer.  We assume that there are some functions $L(M)$ and $R(M)$
that specify a star's luminosity and radius in terms of its mass, and
that the volume-limited binary mass ratio distribution, $f(q)$, is
independent of the primary's mass.  We also allow arbitrary true rate
densities for singles, primaries, and secondaries ($\Gamma_0,
\Gamma_1, \Gamma_2$).  We presume that the observers always take the
properties of a binary system to be those of the primary.

Given this laundry-list of assumptions, a general formula for the
apparent rate density follows:
\begin{align}
    \notag
    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
    \left\{ \Gamma_0(r\a, M\a)+ 
    \frac{{\rm BF}}{1 - {\rm BF}}
    \left[ \int_0^1 \mathrm{d}q \,
           \frac{f(q)}{\mathcal{A}^3}\cdot
           \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}},
    M\a\right)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
        \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
    {R(qM\a) \over R(M\a)}
    q^{-1/3} \right]	\right\},
    \label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction,
and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms
for primaries [secondaries], whose functional dependences are omitted
for notational simplicity.  The dilution terms can be written
\begin{equation}
    \mathcal{A}(q, M\a)
    = \sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
    = (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
  \mathcal{B}(q, M\a)
  = {R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }
  = q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto
R^\alpha$ (the former are more general).  The rate densities depend on
both apparent radius and mass because even if the primaries and
singles were to have fixed mass, the mass of secondaries would vary,
and so this dependence cannot be immediately omitted.

A derivation of Equation~\ref{eq:general_Gamma_a} is given in the
\hyperref[sec:appendix]{Appendix}; its qualitative features are the
same as from our simple model
(Equation~\ref{eq:model_1_apparent_rate_density}).  The terms inside
the curly braces $\{ \ldots \}$ are the sum of the apparent rate
densities from singles, primaries, and secondaries.  The contribution
from singles is not affected by binarity.  In the contributions from
primaries and secondaries, planets with $(r\a, M\a)$ are associated
with systems of different planetary and stellar properties, as
determined by the mass ratio $q$ of each binary.  This corresponds to
true planet radii and stellar masses $(r\a/\mathcal{A},M\a)$ for
primaries, and $(r\a/\mathcal{B},qM\a)$ for secondaries.  These
contributions are then integrated over the mass ratio distribution
including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$,
discussed further below. Finally, the latter term in the apparent rate
density of secondaries comes from a correction for the overestimated
transit probability.

\paragraph{Ratio of searchable binaries to singles}

>>>>

The astronomers then assume that all stars are single.  In particular
they do not have accurate enough parallaxes to tell that some of the
stars are apparently overluminous.  They want to compute the number of
planets with size $r$ per star of mass $M$.  If the total number of
stars for which such planets could be detected ($N_\star$) and the
number of detected planets ($N_{\rm det}$) are both large, then the
astronomers' estimate for the occurrence rate ($\Lambda$) is simply
\begin{equation}
\Lambda = \frac{N_{\rm det}}{N_\star}
                    \times \frac{1}{p_{\rm tra}},
\label{eq:occ_rate_simple}
\end{equation}
where $p_{\rm tra}$ is the geometric transit probability, needed to
account for the fact that most planetary orbits are not aligned close
enough with our line of sight to produce transits.

@@

@@

Since the effects of binarity are most pronounced when the two
components are similar, we begin by considering a universe in which
all stars are identical, with mass $M$, radius $R$, and luminosity
$L$.  Some fraction of them exist in twin binaries. All planets have
size $r\p$.  In this scenario, stars are never misclassified because
the combined light of a binary has the same color and spectrum as a
single star.  We further assume that planets occur around single stars
and members of binaries at the same rate, $\Lambda(r\p)$.

The only type of planet in this universe produces a transit signal of
amplitude $\delta_{\rm obs} = (r\p/R)^2$ when the host is a single
star.  Our naive observers try to measure the occurrence rate of these
planets.  They identify all the ``stars'' in their sample that appear
to be searchable for such a signal, given the size of their telescope.
These transits are detected within a certain maximum 
distance~\citep[see][]{pepper_using_2003,pepper_searching_2005}, which from
Equation~\ref{eq:S_N_thresh} scales as
\begin{equation}
  d_{\rm max} \propto \delta_{\rm obs} \cdot L_{\rm sys}^{1/2}.
  \label{eq:dmax}
\end{equation}
Assuming that stars are uniformly distributed in space, the number of
searchable stars $N_\star$ is then proportional to
\begin{equation}
    N_\star \propto n_i \delta_{\rm obs}^3 L_{\rm sys}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n_i$ is the number per unit volume of single stars, or
binary systems.

This selection process inadvertently admits some binaries.  Since the
binaries are twice as luminous as singles, they are included out to a
distance that is larger by a factor of $\sqrt{2}$, and if they have
transiting planets then the signals have an amplitude of
$(r\p/R)^2/2$.  To detect this half-strength signal, the observers
need the noise level to be lower by a factor of two, which means the
flux must be four times higher than that of a single star at distance
$d_0$.  This is true of single stars within a distance $d_0/2$, and
binaries within a distance $d_0\sqrt{2}/2$.
Furthermore the observers will consider any such shrunken signals to
represent planets of a different type, smaller in radius by a factor
of $\sqrt{2}$. These searchable volumes are illustrated in 
Figure~\ref{fig:model_1_volumes}.

Putting it all together, the {\it apparent} occurrence rate of planets
of radius $r\p$ will be
\begin{equation}
    \Lambda\a(r\p) = 
        \frac{\Lambda(r\p)~n\s d_0^3}
        {n\s d_0^3 + n\b (d_0\sqrt{2})^3}
\end{equation}
where $n\s$ and $n\b$ are the number densities of single stars and
binary stars, respectively, in the local neighborhood.  This apparent
rate is larger than the true rate by a factor
\begin{equation}
    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 
        \frac{1}{1 + 2^{3/2}(n\b/n\s)}.
    \label{eq:correction_rp}
\end{equation}
The observers will also claim to have discovered a new type of planet
with radius $r\p/\sqrt{2}$ and an occurrence rate given by
\begin{equation}
\label{eq:correction_diluted_rp}
    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)}
    =
    \frac{2n\b (d_0\sqrt{2}/2)^3}
      {n\s (d_0/2)^3 + n\b (d_0\sqrt{2}/2)^3}
    =
    \frac{2\cdot2^{3/2}(n\b/n\s)}{1 + 2^{3/2}
    (n\b/n\s)}.
\end{equation}

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Apparent occurrence rate $\Lambda\a$, and occurrence rate for
        singles $\Lambda_0$, for a model with one type of star, one
        type of planet, and twin binaries (same as
        Figure~\ref{fig:model_1_volumes}).  We assume a twin binary
        fraction of $0.05$, and that single, primary, and secondary
        stars host planets at equal rates.  If the true planet radius
        is $r\p$, all planets detected in binaries will have apparent
        radii $r\a = r\p/\sqrt{2}$; Equation~\ref{eq:ratios} gives the
        normalizations.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

We can now assess the severity of these errors, given the
binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
fraction to be 0.44, where multiplicity fraction is defined as
the fraction of systems in a volume-limited sample that are multiple.
Since we assume all multiple systems are binaries, this implies
\begin{equation}
    \frac{n\b}{n\s + n\b} \approx 0.44,
\end{equation}
which corresponds to a specific $n\b/n\s$.  Of course not all of these
binaries are close to being ``twin'' binaries as we have assumed in
our simple calculation. Perhaps only a tenth of them have pairs of
stars close enough in their basic properties to produce errors as
significant as those we have been considering.  Thus, an appropriate
estimate for $n\b/(n\s+n\b)$ is of order $0.05$, leading to
\begin{equation}
    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 0.87,~~
    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)} = 0.26.
    \label{eq:ratios}
\end{equation}
All together the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is
characteristic of many of our more complicated models, as well.

\subsection{Formula Based on Apparent Rate Density}
\label{sec:model_1_density}

There is a different way to conceptualize the preceding results that
will be useful in the subsequent discussion.  Here we broaden the
discussion to consider a spectrum of planet sizes, by introducing the
occurrence rate density
\begin{equation}
    \Gamma(r) \equiv \frac{d\Lambda}{dr},
\end{equation}
the average number of planets per star per unit planet radius.

To clarify our terminology, we define ``apparent properties'' as the
properties that one would infer about a system under the assumption
that the host star is single. For instance, the  ``apparent planet
radius'', $r\a$, is the planet radius that one would infer from a
transit signal, assuming that the host star is single.  The observed
transit depth is given by the ratio of the apparent planet radius and
the apparent stellar radius, $R\a$:
\begin{equation}
  \delta_{\rm obs}
  = \left(\frac{r\a}{R\a}\right)^2
  = \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over
          L_{\rm sys}},
  \label{eq:delta_obs_general} 
\end{equation}
for $r$ the planet radius, $R_{\rm host}$ ($L_{\rm host}$) the host
star's radius (luminosity), and $L_{\rm sys}$ the entire system's
luminosity. This gives $r\a=r\p/\sqrt{2}$ in our ``twin binary''
model.

With this definition we may say that naive observers are measuring
$\Gamma\a(r\a)$, the apparent occurrence rate density of planets with
an apparent radius of $r\a$.  Analogous to
Equation~\ref{eq:occ_rate_simple},  
\begin{equation}
  \Gamma\a(r\a) = \frac{n_{\rm det}(r\a)}{N_\star(r\a)}
      \times \frac{1}{p_{\rm tra}},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}$ is the number of detected planets, per unit $r\a$,
with apparent radius $r\a$.  In
Equation~\ref{eq:apparent_rate_density}, we neglect the dependence on
stellar mass since all stars in this model have the same properties.
Since $\delta_{\rm obs}$ and $r\a$ are related by $R\a$, which is
simply assumed by an observer, measuring $\Gamma\a(r\a)$ is equivalent
to measuring the true occurrence rate density of {\it transit signals}
of amplitude $\delta_{\rm obs}$.

Let us evaluate the contributions to $n_{\rm det}$ from singles and
binaries.  As in the previous subsection, for each apparent planet
radius $r\a$, the observers select $N_\star(r\a)$ unresolved
point-sources on sky, based on Equation \ref{eq:dmax}.  If we let $\mu
\equiv N\star^{\rm b}(r\a)/N_\star^0(r\a)$ be the ratio of the number
of searchable binary systems to single systems, then the number of
single and binary point-sources thought to be searchable are
\begin{equation}
  \frac{N_\star(r\a)}{1+\mu}~~{\rm and}~~\frac{\mu N_\star(r\a)}{1+\mu},
\end{equation}
respectively.  Earlier we showed that due to Malmquist bias, $\mu =
2^{3/2}(n\b/n\s)$.

We further stipulate that the true occurrence rate densities for
planets around single stars, primaries, and secondaries are
$\Gamma_0(r)$, $\Gamma_1(r)$, and $\Gamma_2(r)$, respectively.  
Then single stars contribute
\begin{equation}
  n_{\rm det}^0(r\a) = 
    {N_\star(r\a) \over {1+\mu}} p_{\rm tra} \Gamma_0(r\a)
  \label{eq:n0}
\end{equation}
planet detections per unit $r\a$.  We can similarly compute the number
of planet detections from binaries.  Since $r\p=\sqrt{2}r\a$ for
planets in twin binaries, 
\begin{equation}
  n_{\rm det}^1(r\a)\mathrm{d}r\a =
      {\mu N_\star(r\a) \over {1+\mu}} p_{\rm tra}
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1}
\end{equation}
detections come from primaries, and
\begin{equation}
  n_{\rm det}^2(r\a)\mathrm{d}r\a =
      {\mu N_\star(r\a) \over {1+\mu}} p_{\rm tra}
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n2}
\end{equation}
from secondaries.  Here the transit probability $p_{\rm tra}$ is the
same in all three cases because the stars are all identical.

Using Equation~\ref{eq:apparent_rate_density}, the apparent rate
density reported when ignoring binarity is
\begin{equation}
	\label{eq:formula_twin_binary}
  \Gamma\a(r\a) =
    \frac{1}{1+\mu}\,\Gamma_0(r\a) +
    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_1(\sqrt{2}r\a) +
    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_2(\sqrt{2}r\a).
\end{equation}
If we further assume 
\begin{equation}
	\Gamma_i=Z \cdot \delta(r\a-r\p)
\end{equation} 
as we did in the previous ``one planet" example,
the above apparent rate density reduces to
\begin{align}
    \Gamma\a(r\a) &= Z \left[
    \frac{1}{1+\mu} \cdot
    \delta(r\a-r\p)  +
    \frac{2\mu}{1+\mu} \cdot
    \delta\left(r\a-\frac{r\p}{\sqrt{2}} \right) \right].
    \label{eq:model_1_apparent_rate_density}
\end{align}
Integrating over $r\a$, this yields
\begin{equation}
	\Lambda\a(r_{\rm p})=\frac{Z}{1+\mu},\quad
	\Lambda\a(r_{\rm p}/\sqrt{2})=\frac{2\mu Z}{1+\mu},
\end{equation}
which reproduce Equations~\ref{eq:correction_rp}
and~\ref{eq:correction_diluted_rp}.

\begin{comment}
    The ratio of the apparent to single star rate
    densities,
    \begin{equation}
        X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)}
          \right|_{r\a \rightarrow r},
    \end{equation}
    can then be evaluated as a ``correction factor''.  At the true and
    diluted planet radii, $X_\Gamma(r\p)=1/(1+\mu)$ and
    $X_\Gamma(r\p/\sqrt{2})=2\mu/(1+\mu)$.  This yields a correction
    $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).
    All together the various effects produce biases of order 10\% in the
    occurrence rates.  
\end{comment}

\begin{comment}
    \subsection{One type of star, two types of planets}

@@

    Following an identical line of reasoning as in
    Section~\ref{sec:model_1}, the apparent rate density can be written
    \begin{align}
        \notag
        \Gamma\a(r\a) &=
        \frac{1}{2(1+\mu)} \left[
        Z_0 \cdot \delta(r\a - r\p)
        +
        \left[Z_0 + \mu (Z_1 + Z_2)
        \right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
        \right. \\
        &\quad\quad\quad\quad\quad\quad\quad\quad+
        \left.
        \mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
        \right].
        \label{eq:two_radii_twins}
    \end{align}
    Just as in Equation~\ref{eq:model_1_apparent_rate_density}, the
    $N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
    However, there are now three detected planet sizes.  Also different is
    that two populations contribute at $r\a = r\p/\sqrt{2}$: the first
    population is singles with $r=r\p/\sqrt{2}$, and the second is twin
    binaries with $r=r\p$.  Both populations are detected out to the same
    maximum searchable distance.  More generally, at any given apparent
    radius, there will be contributions from both singles, primaries, and
    secondaries~---~but the relative weights between these contributions
    will depend on the underlying occurrence rates.
\end{comment}

@@

To generalize the procedure of Section~\ref{sec:model_1_density} to binaries
with varying mass ratios, we consider an SNR-limited transit survey in which
stars can have arbitrary properties.  We assume that there are some functions
$L(M)$ and $R(M)$ that specify a star's luminosity and radius in terms of its
mass, and that the volume-limited binary mass ratio distribution, $f(q)$, is
independent of the primary's mass.  We also allow arbitrary true rate densities
for singles, primaries, and secondaries ($\Gamma_0, \Gamma_1, \Gamma_2$).  We
presume that the observers always know the true masses of singles and
primaries, and that they take the primary's properties to be those of an
unresolved binary.

Due to the varying mass ratios, we need the following modifications to Equation
\ref{eq:formula_twin_binary}:
\begin{enumerate}
%
  \item The number of binary systems with mass ratio $(q,
  q+\mathrm{d}q)$ in the selected sample is now
  (Equation~\ref{eq:dmax}):
  \begin{equation}
      {N_\star(r\a)\over{1+\mu}}\times {n_{\rm b}\over n_{\rm s}}
      \left[{L_{\rm sys}(M\a, q) \over L(M\a)}\right]^{3/2}
      f(q)\,\mathrm{d}q,
  \end{equation}
  where
  \begin{equation}
      \mu({\rm BF},M\a)= 
      %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
      \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm sys}(M\a, q)
      \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
      \label{eq:mu_general}
  \end{equation}
  These should replace ${\mu N_\star(r\a)/(1+\mu)}$ in Equations
  \ref{eq:n0}--\ref{eq:n2}. Then the result needs to be integrated
  over $q$.

  \begin{figure}[!tb]
      \centering
      \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
      \caption{
          The mass ratio distribution for a magnitude-limited sample of
          binary stars, in which the underlying volume-limited
          distribution is uniform, qualitatively similar to Figure~16 of
          \citet{raghavan_survey_2010}.  At a given observed transit
          depth, the searchable binaries in a transit survey are
          magnitude-limited. For this figure, we assume $L\propto
          M^{3.5}$
      }
      \label{fig:q_distribn_mag_limited}
  \end{figure}

  As we showed earlier, this can be understood as a Malmquist bias: in
  the magnitude-limited sample of searchable binaries, those with
  larger mass ratios are overrepresented by a factor or
  $\left[{L_{\rm sys}(M\a, q)/L(M\a)}\right]^{3/2}$ because they are
  brighter. We show this magnitude-limited mass ratio distribution
  for the flat $f(q)$ in Figure~\ref{fig:q_distribn_mag_limited}.  In
  Monte Carlo simulations of transit surveys, it is important to
  draw binaries from an appropriately biased mass-ratio
  distribution~\citep[\textit{e.g.},][]{
    bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.
%
  \item The relationship between $r\a$ and $r$ are different.  From
    Equation~\ref{eq:delta_obs_general}, $r=\mathcal{D}_{1/2}r\a$ for
    primaries and secondaries, where
  \begin{equation}
      \mathcal{D}_1(q, M\a)
      = \sqrt{L_{\rm sys}(M\a, q) \over L(M\a) }
      = (1+q^\alpha)^{1/2},
  \end{equation}
  and
  \begin{equation}
    \mathcal{D}_2(q, M\a)
    = {R(qM\a)\over R(M\a)}\sqrt{L_{\rm sys}(M\a, q) \over L(qM\a)} 
    = q (1+q^{-\alpha})^{1/2}.
  \end{equation}
  So $\sqrt{2}r\a$ in Equations~\ref{eq:n1} and~\ref{eq:n2} needs to be
  replaced with $\mathcal{D}_1r\a$ and $\mathcal{D}_2r\a$, respectively.

  \item The transit probability around secondaries are smaller than
  that around primaries, the latter of which is the same as
  primaries under our assumption. At a fixed orbital period, this
  changes $p_{\rm tra}$ in Equation~\ref{eq:n2} by a factor of
  \begin{equation}
    {R(qM\a) \over R(M\a)}q^{-1/3}.
  \end{equation}

\end{enumerate}
